Making Sequential Programs Deterministic

### 2019-03-30 experiments.tex
bib refs for tools

\section{Evaluation}
\subsection{NONDEX case study}
Methodology:
\begin{itemize}
    \item Objective: Measure recall.
    \item Benchmarks from NONDEX paper.
    \item That paper gives flaky test class and source of flakiness (nondeterministic method call).
    \item Look at the source method under test.
    \item annotate the local arrays and collections (This has been mostly sufficient for recall)
\end{itemize}

@@

\begin{itemize}
    \item Refer to table and describe it.
    \item P7: same source causing multiple tests to be flaky
    \item Example for class.GetDeclaredMethod() and show annotations
    \item Example for HashMap.entrySet() and show annotations.
    \item qualitative comparison: orthogonal techniques (reporting tests vs reporting source locations).
    \item From NonDex paper: "manually inspecting these failures was rather challenging"
\end{itemize}

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{3cm}|p{4cm}|p{2cm}|p{1.5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg & \#annotations & Annotation type  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible &  &   \\
        P2 & MI &  &  &  &  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible&  &  \\ 
        P4 & MI &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\
        P7(test error) & Yes & checker/ tests/ determinism/P71.java: 5 & return type incompatible &  &  \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible &  &  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible &  &  \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible &  &  \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible & &  \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P9 & MI &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P11 & MI &  &  &  &  \\
        P12 & MI &  &  &  &  \\
        P13 & crash &  &  &  &  \\
        P14 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible &  &  \\
        P17 & Yes &  &  &  &  \\
        P18 & src &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\ \hline
    \end{tabular}
\end{table}

>>>>

\section{Evaluation}
\begin{itemize}
    \item goals of evaluation: Compare with NonDex and Deflaker
    \item Quantitative comparison: \theDeterminismChecker finds all bugs reported by NonDex and Deflaker?
    \item Qualitative study of the issues discovered.
    \item System info: 2.3 GHz Intel Core i5, 8 GB 2133 MHz
\end{itemize}

\subsection{Running NONDEX on Randoop}
To evaluate how existing tools perform on large programs, we ran NONDEX~\cite{nondex-tool} on Randoop~\cite{randoop-tool}.
\begin{itemize} 
    \item Ran randoop with NonDex, instructions from cite.
    \item didn't find any flakiness issues in the FULL mode.
    \item \todo{check if the bugs discovered by \theDeterminismChecker have test coverage}
\end{itemize}

\subsection{NONDEX case study}
Methodology:
\begin{itemize}
    \item Objective: Measure recall.
    \item Benchmarks from NONDEX paper.
    \item That paper gives flaky test class and source of flakiness (nondeterministic method call).
    \item Look at the source method under test.
    \item annotate the local arrays and collections (This has been mostly sufficient for recall)
    \item exceptions: unbuildable handlebars
    \item the reported source of nondeterminism couldn't be found in the source code.
    \item \todo{P4, P12 and P21}
\end{itemize}

@@

\begin{itemize}
    \item Refer to table and describe it.
    \item P7: same source causing multiple tests to be flaky
    \item Example for class.GetDeclaredMethod() and show annotations
    \item Example for HashMap.entrySet() and show annotations.
    \item qualitative comparison: orthogonal techniques (reporting tests vs reporting source locations).
    \item From NonDex paper: "manually inspecting these failures was rather challenging"
    \item P18 sl4j: nondeterminism in the test case. we provide stub for junit.
    \item Specification for Assert: parameters are annotated as Det
\end{itemize}

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{4cm}|p{5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible \\
        P2 & Yes & YamlWriter.java: [224,28] & cast unsafe  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible \\ 
        P4 & * & Det checker not found  &   \\ 
        P5 & ** & Class.getDeclaredMethods not found &    \\ 
        P6 & Yes & OptionGroup.java: [55,40]  & argument type incompatible \\ 
        P6 & Yes & Option.java: [157,28]  &  assignment type incompatible\\
        P7(test error) & Yes* & checker/ tests/ determinism/P71.java: 5 & return type incompatible \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible   \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible   \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible  \\
        P8 & ** & getDeclaredFields not found &   \\
        P9 & Yes & Printers.java: [269,97]  &  enhancedfor type incompatible \\
        P10 & ** & getDeclaredFields not found  &  \\
        P11 & Yes & MapUtils.java: [20,50]   & enhancedfor type incompatible  \\
        P12 & *  & 0 errors &  \\
        P13 & ** & unbuildable handlebars &  \\
        P14 & Yes  & Maps.java: [91,69] & invalid element type   \\
        P15 & Yes & PkiMessageDecoder.java: [144,29]  &  enhancedfor type incompatible  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible  \\
        P17 & Yes & JSONObject.java: [674,51]  & assignment type incompatible  \\
        P18 & Yes & SubstitutableLoggerTest.java: [67,61]   & enhancedfor type incompatible  \\
        P19 & Yes & DataDictionaryEventSource.java: [73,78]  &  enhancedfor type incompatible  \\
        P20 & Yes & SaverImpl.java: [43,69]  &  return type incompatible  \\
        P21 & * & 0 errors &   \\ \hline
    \end{tabular}
\end{table}
